Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-21 analyses/scripts/orv_sys_rev_supplementary.Rmd
Removed redundant code

```{r echo=FALSE}
#' Count the number of each author affiliation type per year (including FMD)
collap_types_by_year <- data_without_fmd %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'Purely academic', 
                                         'Mixed')
                                 )
         ) %>% 
  count(year_aggreg, collab_type, , name = 'num_of_studies') %>% 
  pivot_wider(names_from = collab_type, values_from = num_of_studies)
        name = 'total_publications'
        ) %>% 
  pivot_wider(names_from = collab_type, values_from = total_publications)

>>>>

```{r echo=FALSE}
#' Count the number of each author affiliation type per year (including FMD)
collap_types_by_year <- data_without_fmd %>% 
  mutate(year_aggreg = as.numeric(ifelse(publication_year < 2006, 
                                         2005, 
                                         publication_year
                                         )
                                  ), 
         collab_type = as_factor(if_else(author_affiliation_type == 'academic_institutions', 
                                         'Purely academic', 
                                         'Mixed')
                                 )
         ) %>% 
  count(year_aggreg, collab_type, , name = 'num_of_studies') %>% 
  pivot_wider(names_from = collab_type, values_from = num_of_studies)
